---
title: "Sentiment Analysis"
author: "Jinbo Niu"
date: "2023/4/25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# 情绪分析
## 情绪词典
library(dplyr)
library(tidytext)
library(janeaustenr)
library(stringr)
#sentiments
#get_sentiments("afinn")
#get_sentiments("nrc")
#get_sentiments("bing")

```

### Inner Join 情感分析(通过NRC)
```{r}
library(tidytext)
tidy_books <- austen_books()%>%
  group_by(book)%>%
  mutate(linenumber = row_number(),chapter = cumsum(str_detect(text,regex("^chapter[\\divxlc]",ignore_case = TRUE))))%>%
  ungroup()%>%unnest_tokens(word,text)
```

## Joy的词 inner join
```{r}
nrcjoy <- get_sentiments("nrc")%>%filter(sentiment == "joy")
tidy_books %>% filter(book == "Emma")%>%
  inner_join(nrcjoy)%>%count(word,sort = TRUE)
```

## 对Jane的作品每80行进行正负情感分析
```{r}
library(tidyr)
janeaustensentiment <- tidy_books%>%
  inner_join(get_sentiments("bing"))%>%
  count(book,index = linenumber%/%80,sentiment)%>%
  spread(sentiment,n,fill = 0)%>%
  mutate(sentiment = positive-negative)
  
```
# Visualize it
```{r}
library(ggplot2)

ggplot(janeaustensentiment,aes(index,sentiment,fill = book))+
  geom_col(show.legend = FALSE)+
  facet_wrap(~book,ncol = 2,scales = "free_x")
```

# Compare three dictionaries
```{r}
library(tidyr)
#we first choose pride and prejudice as the text for this comparison
pride_prejudice <- tidy_books %>% filter(book == "Pride & Prejudice")

bing_and_nrc <- bind_rows(pride_prejudice%>%inner_join(get_sentiments("bing"))
                                        %>%group_by(index = linenumber%/%80)
                          %>%mutate(method = "Bing et. al"),
                          pride_prejudice %>% inner_join(get_sentiments("nrc")
                          %>%filter(sentiment %in% c("positive","negative")))%>%
                            mutate(method = "NRC"))%>%
                          count(method,index = linenumber%/%80, sentiment)%>%
                      spread(sentiment,n,fill = 0)%>%
                mutate(sentiment = positive-negative)


afinn <- pride_prejudice %>% inner_join(get_sentiments("afinn"))%>%
  group_by(index = linenumber%/%80)%>%summarise(sentiment = sum(value))%>%
  mutate(method = "afinn")

```

#visualize it
```{r}
library(ggplot2)
bind_rows(afinn,bing_and_nrc)%>%
  ggplot(aes(index,sentiment,fill = method))+geom_col(show.legend = FALSE)+
  facet_wrap(~method,ncol = 1,scales = "free_y")
                                                    
```

## comparison between NRC and Bing
```{r}
#nrc
get_sentiments("nrc")%>%
  filter(sentiment %in% c("positive","negative"))%>%count(sentiment)

get_sentiments("bing")%>%count(sentiment)
```
## Most common words in three dictionaries respectively
```{r}
bing_word_counts <- tidy_books %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word,sentiment,sort = TRUE)%>%ungroup

bing_word_counts
```


```{r}
bing_word_counts %>% group_by(sentiment)%>% 
  top_n(10) %>% ungroup()%>%
  mutate(word = reorder(word,n))%>%
  ggplot(aes(word,n,fill = sentiment))+geom_col(show.legend = FALSE)+
  facet_wrap(~sentiment,scales = "free_y")+labs(y = "Contribution to sentiment",x = NULL)+
  coord_flip()

```

#Define stop words
```{r}
custom_stop_words <- bind_rows(data_frame(word = c("miss"),lexicon = c("custom")),stop_words)

custom_stop_words
```

## Word Cloud
```{r}
#The most common words in Jane Austen's books
library(wordcloud)
tidy_books %>% anti_join(stop_words)%>%
    count(word)%>% with(wordcloud(word,n,max.words = 100))

```
#comparison cloud
```{r}
#The most positive and negative words in Jane Austen's books
library(reshape2)
tidy_books%>%
  inner_join(get_sentiments("bing")) %>%
  count(word,sentiment,sort = TRUE)%>%
  acast(word~sentiment,value.var = "n",fill = 0)%>%
  comparison.cloud(colors = c("gray20","gray80"),max.words = 100)

```

## Text Units besides words
```{R}
#unnest_token正则表达式
austen_chapters <- austen_books()%>%
  group_by(book)%>%
  unnest_tokens(chapter,text,token = "regex",pattern = "Chapter|CHAPTER[\\dIVXLC]")%>%
  ungroup()

austen_chapters %>% group_by(book)%>%
  summarise(chapters = n())
```
#Which chapter is the most negative and which is the most negative words in terms of each book
```{r}
bingnegative <- get_sentiments("bing")%>%filter(sentiment == "negative")

wordcounts <- tidy_books %>%
  group_by(book,chapter)%>%
  summarize(words = n())

tidy_books%>% semi_join(bingnegative)%>%group_by(book,chapter)%>%
  summarize(negativewords = n())%>%
  left_join(wordcounts,by = c("book","chapter"))%>%
  mutate(ratio = negativewords/words)%>%
  filter(chapter!=0)%>%
  top_n(1)%>%ungroup()
```

