---
title: 'Chapter 3: word frequency'
author: "Jinbo Niu"
date: "2023/5/6"
output: html_document
---
# IDF(Inverse document frequency)
```{r}
library(dplyr)
library(janeaustenr)
library(tidytext)


```
## Word frequency in Jane austen's work
```{r}
book_words <- austen_books()%>%
  unnest_tokens(word,text)%>%count(book,word,sort = TRUE)%>%ungroup()

total_words <- book_words %>%
  group_by(book)%>%summarise(total = sum(n))

book_words <- left_join(book_words,total_words)

book_words
```

### visualize it

```{r}
library(ggplot2)

ggplot(book_words,aes(n/total,fill = book))+
  geom_histogram(show.legend = FALSE)+
  xlim(NA,0.0009)+facet_wrap(~book,ncol = 2,scales = "free_y")
                                                          
```
#Zipf 定律：词出现的频率与其排名呈反比

##Zipf Law in Jane Austen's work
```{r}
freq_by_rank <- book_words %>%
  group_by(book)%>%
  mutate(rank = row_number(),`term frequency` = n/total)

freq_by_rank
```
```{r}
library(ggplot2)
freq_by_rank %>%ggplot(aes(rank,`term frequency`,color = book))+
  geom_line(size = 1.1,alpha = 0.8,show.legend = FALSE)+
  scale_x_log10()+scale_y_log10()

```
#Zipf indicator in Jane Austen's work
```{r}
rank_subset <- freq_by_rank %>%
  filter(rank<500,rank>10)

lm(log10(`term frequency`)~log10(rank),data = rank_subset)

```
The slope is close to -1, so it generally fits the Zipf principle.
Now let's visualize it.

```{r}
rank_subset%>%
  ggplot(aes(rank,`term frequency`,color = book))+
  geom_abline(intercept = -0.62,slope = -1.1,color = "grey50",linetype = 2)+
  geom_line(size = 1.1, alpha = 0.8,show.legend = FALSE)+
  scale_x_log10()+scale_y_log10()

```
### Bind-tf-idf
bind_tf_idf function is in tidytext package
```{r}
book_words <- book_words%>%
  bind_tf_idf(word,book,n)

book_words

```
```{r}
#since total is not necessary for bind_tf_idf function, so we won't select it when exploring the tf-idf with bind_tf_idf function
book_words %>%
  select(-total)%>%
  arrange(desc(tf_idf))

```
#Visualize words with the highest tf-idf
```{r}
book_words %>%
  arrange(desc(tf_idf))%>%
  mutate(word = factor(word,levels = rev(unique(word))))%>%
  group_by(book)%>%
  top_n(15)%>%
  ungroup()%>%
  ggplot(aes(word, tf_idf, fill = book))+geom_col(show.legend = FALSE)+
  labs(x = NULL,y = "tf-idf")+facet_wrap(~book,ncol = 2,scales = "free")+
  coord_flip()
```
## Physics work
This section will explore the difference between literature work and physics texts
```{r}
library(gutenbergr)
physics <- gutenberg_download(c(37729,14725,13476,5001),meta_fields = "author")
```
```{r}
physics_words <- physics%>%
  unnest_token(word,text)%>%
  count(author,word,sort = TRUE)%>%
  ungroup()
```

```{r}

```
